On change of priors in one-vs-one classification methods

### 2025-05-21 experiment.tex
Revised introduction; added graph to Experiment 1
Better caption

For preprocessing we first removed features that were constant across classes. Then we projected the data using PCA to the subspace for which corresponding singular values were at least $1/1000$. We used PCA without scaling or centering since the datasets' features were already normalized to interval $[-1,1]$.

@@

>>>>

For preprocessing we first removed features that were constant across classes. Then we projected the data using PCA to the subspace for which corresponding singular values were $> tol$, where $tol$ is a hyper-parameter of an experiment. We used PCA without scaling or centering since the datasets' features were already normalized to interval $[-1,1]$.

@@

\begin{figure}
	\includegraphics{graphs/exp1-plot1.pdf}
	\caption{0-1 score plotted against the logarithm of $tol$ hyper-parameter, evaluated for different datasets.}
	\label{fig:exp1-plot1}
\end{figure}
